---
title: "Anonymizing Data"
author: "Vicky Steeves"
date: "October 11, 2017"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

This tutorial will go over how to anonmyize data with R, then share a reproducible package. I adapted this tutorial from Jan Gorecki's [blog post](https://gitlab.com/jangorecki/jangorecki.gitlab.io/blob/master/_posts/2014-11-07-Data-Anonymization-in-R.md).

First, we need to load in the three depedencies:

```{r}
library(data.table)
library(digest)
library(knitr)
```

Then we need to read the data and we'll display it in our Notebook nicely using kable().

```{r}
SURV<-read.csv(file=file.path("../data/2017-10-11_Dataset.csv"), header=TRUE)
kable(head(SURV))
```

Next, we'll use a function called `anonymizeCRC` to apply a unique hash to each value in a given column, using the crc32 algorithm. You can read more about [digest()](https://cran.r-project.org/web/packages/digest/digest.pdf).

```{r}
anonymizeCRC <- function(x, algo="crc32"){
  unq_hashes <- vapply(unique(x), function(object) digest(object, algo=algo), FUN.VALUE="", USE.NAMES=TRUE)
  unname(unq_hashes[x])
}
```

Pick columns

```{r}
# choose columns to mask
cols_to_mask <- c("NAME","ADDRESS","POSTAL.CODE")

# backup original data
SURV_ORG <- copy(SURV)

# anonymize
SURV[cols_to_mask] <- lapply(SURV[cols_to_mask], anonymizeCRC)

# pretty print
kable(head(SURV))
```

We can use other hashing algorithms, though! We'll use a function called `anonymizeMD` to apply a unique hash to each value in a given column, using the md5 algorithm.


```{r}
anonymizeMD <- function(x, algo="md5"){
  unq_hashes <- vapply(unique(x), function(object) digest(object, algo=algo), FUN.VALUE="", USE.NAMES=TRUE)
  unname(unq_hashes[x])
}
```

We will pick the columns we want to anonmyize -- in this case, NAME, POSTAL.CODE, and ADDRESS, and put feed them into anonymizeMD. I also want to backup the original table just in case I mess up!

```{r}
# choose columns to mask
cols_to_mask <- c("NAME","ADDRESS","POSTAL.CODE")

# backup original data
SURV_ORG <- copy(SURV)

# anonymize
SURV[cols_to_mask] <- lapply(SURV[cols_to_mask], anonymizeMD)

# pretty print
kable(head(SURV))
```
